Bird beak's elaboration and innovation

### 2022-07-14 Analysis/03-Elaboration_innovation_analysis.Rmd
Update 03-Elaboration_innovation_analysis.Rmd

>>>>

## Measuring ellipse's statistics

For each group, we can calculate:

 * It's orientation (angle) relative to the whole phylogeny
 * It's (dis)alignment relative to the the phylogeny
 * It's distance from the centroid of the phylogeny

We can also calculate for each group:

 * It's angle internal variance (as a proxy for internal variance)
 * It's axis significance (Andrew's bit)

### Groups compared to the phylogeny

```{r}
## Measuring fun
ellipse.stats <- function(data) {
    ## Get the groups list
    groups_list <- unlist(apply(matrix(c(1:(n.subsets(data)-1), rep(n.subsets(data),(n.subsets(data)-1))), ncol = 2), 1, list), recursive = FALSE)

    ## Renanme the phylogeny subset
    names(data$subsets)[n.subsets(data)] <- "phy"

    ## Measure the disparities
    results <- list(
        angles     = dispRity(data, metric = as.covar(projections.between), measure = "degree", between.groups = groups_list),
        alignments = dispRity(data, metric = as.covar(disalignment, VCV = c(FALSE, TRUE), loc = c(TRUE, FALSE)), between.groups = groups_list),
        distances  = dispRity(data, metric = group.dist, probs = c(0.5), between.groups = groups_list)
    )
    return(results)
}

## General measurement
super_orders_stats <- ellipse.stats(superorder_shapespace)
orders_stats <- ellipse.stats(order_shapespace)

load("../Data/Processed/tip_colours_super_orders.rda")
col <- tip_colours_super_orders
results <- super_orders_stats
## Ploting fun
ploting.stats <- function(results, col) {
    par(mfrow = c(1,3))
    ##
    plot(results[[1]], horizontal = TRUE, las = 1, xlab = "angle", ylab = "", col = col)
    plot(results[[2]], horizontal = TRUE, las = 1, xlab = "disalignment", ylab = "", yaxt = "n", col = col)
    plot(results[[3]], horizontal = TRUE, las = 1, xlab = "distance between centroids", ylab = "", yaxt = "n", col = col)
}

### Groups compared in cherries

### Groups own variance
